Título

### 2012-08-17 novela.tex
Esquelo inicial para una novela escrita en Latex

Texto del capítulo 1
texto texto texto texto texto texto texto texto 
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto 
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto 
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto 
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto 
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto 
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto 
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto 
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto 
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto 
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto 
texto texto texto texto texto texto texto texto
texto texto texto

@@

>>>>

\documentclass[11pt,twoside,openright,a5paper]{book}

\usepackage[a5paper]{geometry}

\usepackage{times}
\usepackage[Lenny]{fncychap}
%\usepackage[Conny]{fncychap}

\usepackage[spanish]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\newcommand{\personaje}{Nombre del personaje}

\title{Título}
\author{Autor}
\date{}

\hyphenation{o-pe-ra-cio-nes}

\begin{document}

\pagestyle{plain}

\maketitle

\tableofcontents

\chapter*{Prólogo}
\addcontentsline{toc}{chapter}{Prólogo}

@@

\chapter{Título Capítulo}
\input{cap1.tex}

\end{document}
